Sex-specific Meta-analysis in MSSM-Penn-Pitt and HBCC ACC/DLPFC

### 2020-07-29 individual-cohorts/graphics_t_statistics.Rmd
store meta-analysis to Synapse

---
title: "Analysis of diferential expression results"
author: "KM and GH"
date: "`r date()`"
output: html_document
---

```{r knit2synapse, eval=FALSE}
# rmarkdown::render("graphics_t_statistics.Rmd")
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/graphics_t_statistics.Rmd",
                                          parentId ="syn22012942",
                                          folderName = 't-statistics across cohorts')
```

@@

```{r store.files, eval=FALSE}
CODE <- Folder(name = "t-statistics across cohorts", parentId = "syn22012942")
CODE <- synStore(CODE)
```

>>>>

---
title: "Sex-specific Meta-analysis in MSSM-Penn-Pitt and HBCC ACC/DLPFC"
author: "KM and GH"
date: "`r date()`"
output: html_document
---

```{r knit2synapse, eval=FALSE}
# rmarkdown::render("graphics_t_statistics.Rmd")
library(synapser)
library(knit2synapse)
synLogin()
knit2synapse::createAndKnitToFolderEntity(file = "individual-cohorts/graphics_t_statistics.Rmd",
                                          parentId ="syn21435176",
                                          folderName = 'Sex-specific Meta-analysis')
```

@@

```{r store.files, eval=FALSE}
CODE <- Folder(name = "Sex-specific Meta-analysis", parentId = "syn21435176")
CODE <- synStore(CODE)
```
